Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-05-13 xrb/paper.tex
more updates

All simulations use adaptive mesh refinement to refine on the
atmosphere (leaving the space between the top of the atmosphere and
upper boundary at low resolution).  In addition to the base grid, we
use up to 3 refinement levels, the first two a factor of 4 finer than
the previous and the last a factor of 2 finer than the previous.
\castro\ subcycles in time, so the finer grids are evolved with a
finer timestep than the coarse grids.  Occasionally the timestep
chosen at the start of a cycle will violate the CFL condition during
the advance of the finer grids.  In this case, we restart the finer
grid evolution with a smaller timestep, subcycling within the larger
timestep hierarchy.  The finest grid in most of our simulations (base
+ 2 refined levels) corresponds to $4096\times 1024$ zones.

@@

\begin{figure*}[t]
\plottwo{flame}{speed}
\caption{\label{fig:flame} Our ``standard'' flame.}
\end{figure*}

>>>>

All simulations use adaptive mesh refinement to refine on the
atmosphere (leaving the space between the top of the atmosphere and
upper boundary at low resolution).  In addition to the base grid, we
use up to 3 refinement levels, the first one a factor of 4 finer than
the previous and the remaining each a factor of 2 finer than the
previous.  \castro\ subcycles in time, so the finer grids are evolved
with a finer timestep than the coarse grids.  Occasionally the
timestep chosen at the start of a cycle will violate the CFL condition
during the advance of the finer grids.  In this case, we restart the
finer grid evolution with a smaller timestep, subcycling within the
larger timestep hierarchy.  We use a CFL number of 0.8 for our
simulations.  \MarginPar{true for all?} The base grid for our standard
simulations is $768\times 192$ zones and the corresponding finest grid
when 3 refinement levels are added would be $12288\times 3072$ zones.
Our standard domain is $1.2288\times 10^5~\mathrm{cm} \times
3.072\times 10^4~\mathrm{cm}$, so we have $10~\mathrm{cm}$ resolution
on the finest grid.  We only refine the fuel layer in the left half of
the domain at the highest resolution (and only down to densities of
$2.5\times 10^4~\gcc$), since this is where we expect the flame to
propagate.  At the start of the simulation, $3.4\%$ of the domain is
at the finest resolution.  This increases to $7.4\%$ by the end of the
simulation, because of the increase in the scale height of the atmosphere
behind the flame.

@@

\begin{figure*}[t]
\plottwo{flame}{speed}
\caption{\label{fig:flame} Our ``standard'' flame. {\color{red} this should be redone for the boosted flame}}
\end{figure*}
